% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage[maxnames=99]{biblatex}
\usepackage{hyperref}

%-----------------------------------------------------------
% Hyperlink setup
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=red            % color of external links
}

%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\fboxsep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


% Bibliography
\bibliography{publications}{}
%\bibliographystyle{plain}

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Anthony Michael Scopatz} & \textbf{\today} \\
The University of Chicago & scopatz@flash.uchicago.edu \\
Chicago, IL, U.S.A. &  \\
\end{tabular*}
\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education \& Employment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
    \ressubheading{The FLASH Center, The University of Chicago}{Chicago, IL}{Postdoctoral Scholar, Astronomy \& Astrophysics Department}{Nov 2011 - present}
    \begin{itemize}
        \resitem{CosmoB: Simulation of magnetic field generation from neutral plasmas using FLASH.}
        \resitem{FLASH4: High-energy density physics capabilities and utilities.}
        \resitem{Simulated Diagnostics: Schlieren, shadowgraphy, Langmuir probes, etc from FLASH.}
        \resitem{OpacPlot: HDF5-based equation of state and opacity file format.}
    \end{itemize}

\item
    \ressubheading{Enthought, Inc.}{Austin, TX}{Scientific Software Developer}{May 2010 - October 2011}
    \begin{itemize}
        \resitem{PlotTool: Time series data visualization for investment bank.}
        \resitem{PivotTable: Data cube configuration, management, and visualization for investment bank.}
        \resitem{WIPP-PA: Waste Isolation Pilot Project Performance Assessment tool for Sandia Nat'l Labs.}
        \resitem{EasyGuide2: Dental implant imaging software for Keystone Dental.}
    \end{itemize}

\item
    \ressubheading{The University of Texas at Austin}{Austin, TX}{Ph.D. Mechanical Engineering, Nuclear and Radiation Engineering Program}{2008 - 2011}
    \begin{itemize}
        \resitem{Adviser: Erich A. Schneider}
        \resitem{Dissertation: Essential Physics for Fuel Cycle Modeling \& Analysis}
        \resitem{Graduated with 3.74 GPA}
    \end{itemize}

\item
    \ressubheading{The University of Texas at Austin}{Austin, TX}{M.S.E. Mechanical Engineering, Nuclear and Radiation Engineering Program}{2006 - 2007}
    \begin{itemize}
        \resitem{Adviser: Erich A. Schneider}
        \resitem{Thesis: Recyclable Uranium Options under the Global Nuclear Energy Partnership}
    \end{itemize}

\item
    \ressubheading{University of California, Santa Barbara}{Santa Barbara, CA}{B.S. Physics}{2002 - 2006}
    \begin{itemize}
        \resitem{Graduated with a Major in Physics and a Minor in Mathematics}
        \resitem{Graduated with 3.34 GPA}
    \end{itemize}
\end{itemize}

\clearpage


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Awards, Grants \& Honours}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \vspace{-2pt}
    \begin{center}\begin{tabular*}{6.6in}{l@{\extracolsep{\fill}}r}
        \multicolumn{2}{c}{Open Spaces Chair for SciPy 2012 \cftdotfill{\cftdotsep} 2012}\\
        \multicolumn{2}{c}{Nuclear Energy University Programs 2012 \#4065 (\$395,000) \cftdotfill{\cftdotsep} 2012}\\
        \multicolumn{2}{c}{Chair of ``Python \& Core Technologies'' Track at SciPy 2011 \cftdotfill{\cftdotsep} 2011}\\
        \multicolumn{2}{c}{PyCon 2010 Program Committee Member\cftdotfill{\cftdotsep} 2010}\\
        \multicolumn{2}{c}{Innovations in Fuel Cycle Research, 2nd place Systems Engineering and Analysis (\$2,500) \cftdotfill{\cftdotsep} 2010}\\
        \multicolumn{2}{c}{Peer Reviewer for Nuclear Engineering \& Design (NED-D-09-00256) \cftdotfill{\cftdotsep} 2009}\\
        \multicolumn{2}{c}{MCNPX Bug \#100 (\$20) \cftdotfill{\cftdotsep} 2009}\\
        \multicolumn{2}{c}{Graduate Travel Award Fund (\$2,000) \cftdotfill{\cftdotsep} 2008}\\
        \multicolumn{2}{c}{George J. Heuer, Jr. Ph.D. Endowed Graduate Fellowship Fund (\$2,500) \cftdotfill{\cftdotsep} 2007 - 2008}\\
        \multicolumn{2}{c}{George J. Heuer, Jr. Ph.D. Endowed Graduate Fellowship Fund (\$2,500) \cftdotfill{\cftdotsep} 2006 - 2007}\\
        \multicolumn{2}{c}{Undergraduate Research Scholarship (\$1,000) \cftdotfill{\cftdotsep} 2005} \\
        \vphantom{E}
\end{tabular*}
\end{center}\vspace*{-16pt}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
    \ressubheading{Postdoctoral Scholar}{The University of Chicago}{High Energy Density Physics}{November 2011 - present}
    \begin{itemize}
        \resitem{Hydrodynamic simulations of laser-target interaction experiments.}
        \resitem{Development of simulated diagnostic tools for FLASH simulations.}
        \resitem{Development of workflow management and reproducibility tools for FLASH.}
    \end{itemize}

\item
    \ressubheading{Graduate Research Assistant}{The University of Texas at Austin}{Nuclear Fuel Cycle \& Reactor Modeling}{August 2006 - August 2011}
    \begin{itemize}
        \resitem{Development of essential physics reactor models, computational nuclear fuel cycle simulations, and information theoretic analysis.}
        \resitem{Documentation of Indonesia and the nuclear fuel cycle (2006).}
    \end{itemize}

\item
    \ressubheading{Summer Internship/Visiting Scientist}{Idaho National Laboratory}{Nuclear Fuel Cycle \& Reactor Modeling}{Summer 2007}
    \begin{itemize}
        \resitem{Modeled the use of recyclable uranium in light water reactors both with respect to the fuel cycle as a whole and to specific components, like the reactor and enrichment facilities.}
    \end{itemize}

\item
    \ressubheading{Undergraduate Research Assistant}{University of California, Santa Barbara}{Terahertz Continuous Wave Spectroscopy}{2002 - 2005}
    \begin{itemize}
        \resitem{Looked at the effect of Terahertz waves on biomacromolecules in water.}
    \end{itemize}

\item
    \ressubheading{Summer Internship/Visiting Scientist}{Los Alamos National Laboratory}{Terahertz Pump-Probe Spectroscopy}{Summer 2004}
    \begin{itemize}
        \resitem{Looked at the effect of Terahertz waves on Erbium-Arsenide on a Gallium-Arsenide substrate.}
    \end{itemize}

\end{itemize}


\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Major Code Projects}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
    \ressubheading{FLASH}{HEDP Developer}{MHD / Plasma Physics}{Nov 2011 - present}
    \begin{itemize}
        \resitem{Modular, parallel multiphysics simulation code for
                 terrestrial and astrophysical plasmas.}
        \resitem{Features include: Uniform Grid, AMR, Ideal Gas EOS, Multimaterial EOS, 
                 Laser Ray Trace.}
        \resitem{Website: \url{http://flash.uchicago.edu/site/}}
    \end{itemize}

\item
    \ressubheading{PyNE}{Lead Developer}{Python for Nuclear Engineering}{April 2011 - present}
    \begin{itemize}
        \resitem{Nuclear data I/O and manipulation}
        \resitem{Kernels for canonical problems (Bateman eq solvers, diffusion eq solvers, etc.)}
        \resitem{Workflow management tools (I/O support for other codes, fundamental data types, etc.)}
        \resitem{Website: \url{http://pyne.github.com/}}
    \end{itemize}

\item
    \ressubheading{PyTables}{Governance Team Developer}{Pythonic Wrapper for HDF5}{July 2011 - present}
    \begin{itemize}
        \resitem{Package for managing hierarchical datasets}
        \resitem{Efficiently and easily copes with extremely large amounts of data}
        \resitem{Website: \url{http://pytables.github.com/}}
    \end{itemize}

\item
    \ressubheading{Bright}{Lead Developer}{Nuclear Fuel Cycle Component Collection}{September 2006 - present}
    \begin{itemize}
        \resitem{Low-level essential physics models for fuel cycle components in C++}
        \resitem{High-level fuel cycle interface in Python}
        \resitem{Graph-based visualization using the Enthought Tool Suite}
        \resitem{Website: \url{http://bright-dev.github.com/bright/}}
    \end{itemize}

\item
    \ressubheading{CHAR}{Lead Developer}{Cross-sections Have Awesome Rates}{May 2008 - present}
    \begin{itemize}
        \resitem{Cross section generator for Bright multi-group reactors.}
        \resitem{Website: \url{http://scopatz.github.com/char/}}
    \end{itemize}

\item
    \ressubheading{SciPy}{Fair-Weather Developer}{Scientific Python Core Library}{January 2011 - present}
    \begin{itemize}
        \resitem{Open-source software for mathematics, science, and engineering}
        \resitem{Website: \url{http://www.scipy.org/}}
    \end{itemize}

\item
    \ressubheading{Enthought Tool Suite}{Developer}{Tools for building scientific applications}{May 2010 - 2011}
    \begin{itemize}
        \resitem{Traits, Chaco, Mayavi}
        \resitem{CodeTools, BlockCanvas, GraphCanvas}
        \resitem{Website: \url{http://code.enthought.com/}}
    \end{itemize}

\end{itemize}



\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Featured Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item \fullcite{Scopatz2012n}

\item \fullcite{Scopatz2012p}

\item \fullcite{Scopatz2012q}

\item \fullcite{Scopatz2009}

\item \fullcite{Li2009b}
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Postdoctoral Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item \fullcite{Romano2013a}

\item \fullcite{Scopatz2012o}

\item \fullcite{Scopatz2012q}

\item \fullcite{Scopatz2012n}

\item \fullcite{Fatenejad2012b}

\item \fullcite{Tzeferacos2012b}

\item \fullcite{Scopatz2012p}

\item \fullcite{Scopatz2012r}

\item \fullcite{Scopatz2011d}

\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Graduate Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item \fullcite{Huff2011}

\item \fullcite{Scopatz2010c}

\item \fullcite{Scopatz2010b}

\item \fullcite{Scopatz2010i}

\item \fullcite{Scopatz2009c}

\item \fullcite{Shropshire2009a}

\item \fullcite{Scopatz2009g} 

\item \fullcite{Scopatz2009}

\item \fullcite{Li2009b}

\item \fullcite{Schneider2008}

\item \fullcite{Scopatz2008c}

\item \fullcite{Schneider2007}

\item \fullcite{Harrison2007}

\end{itemize}

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Undergraduate Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item \fullcite{Prasankumar2005b}

\item \fullcite{Prasankumar2005a}

\item \fullcite{Prasankumar2005}

\item \fullcite{Xu2004}

\item \fullcite{Xu2003}

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Presentations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item \fullcite{Scopatz2012e}

\item \fullcite{Scopatz2012f}

\item \fullcite{Scopatz2012g}

\item \fullcite{Scopatz2012d}

\item \fullcite{Scopatz2012l}

\item \fullcite{Scopatz2012k}

\item \fullcite{Scopatz2012m}

\item \fullcite{Scopatz2012j}

\item \fullcite{Scopatz2012i}

\item \fullcite{Scopatz2012h}

\item \fullcite{Scopatz2011c}

\item \fullcite{Scopatz2011b}

\item \fullcite{Scopatz2011a}

\item \fullcite{Scopatz2011}

\item \fullcite{Preston2011}

\item \fullcite{Scopatz2010h}

\item \fullcite{Scopatz2010g}

\item \fullcite{Scopatz2010f}

\item \fullcite{Scopatz2010a}

\item \fullcite{Scopatz2010l}

\item \fullcite{Scopatz2010j}

\item \fullcite{Scopatz2010d}

\item \fullcite{Scopatz2010e}

\item \fullcite{Scopatz2009d}

\item \fullcite{Scopatz2009f}

\item \fullcite{Scopatz2008b}

\item \fullcite{Harrison2007a}

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Posters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item \fullcite{Scopatz2012c}

\item \fullcite{Flocke2012a}

\item \fullcite{Fatenejad2012a}

\item \fullcite{Scopatz2012a}

\item \fullcite{Scopatz2012b}

\item \fullcite{Tzeferacos2012a}

\item \fullcite{Miranda2011}

\item \fullcite{Scopatz2010k}

\item \fullcite{Schneider2009}

\item \fullcite{Li2009c}
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Teaching Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
    \ressubheading{HDF5 is for Lovers}{SciPy 2012}{Instructor}{July 16 2012}
    \begin{itemize}
        \resitem{Instructed 50+ students in the use \& structure of HDF5 and PyTables.}
        \resitem{\href{http://conference.scipy.org/scipy2012/schedule/tutor_schedule_1.php\#ti-76}{Tutorial Website} \& 
                 \href{http://www.youtube.com/watch?v=Nzx0HAd3FiI}{Video}, 
                 \href{https://github.com/scopatz/scipy2012/tree/master/hdf5}{Source Materials}
                 }
    \end{itemize}

\item
    \ressubheading{Python for Scientific Computing}{Enthought, Inc}{Instructor}{2011}
    \begin{itemize}
        \resitem{Instructed 10 week-long courses on scientific computing in Python at various universities, national labs, \& businesses.}
    \end{itemize}

\item
    \ressubheading{SciPy Tutorial}{SciPy 2011}{Instructor}{July 11 2011}
    \begin{itemize}
        \resitem{Instructed 50 students in the SciPy Python package.}
        \resitem{\href{http://conference.scipy.org/scipy2011/tutorials.php\#anthony}{Website}}
    \end{itemize}

\item
    \ressubheading{Computational Methods in Nuclear Engineering}{The University of Texas at Austin}{Teaching Assistant/Grader}{Aug. 2010 - Dec. 2010}
    \begin{itemize}
        \resitem{Helped students develop and debug their discrete ordinates code throughout the course.}
    \end{itemize}

\item
    \ressubheading{Astronomy 1}{University of California, Santa Barbara}{Undergraduate Teaching Assistant/Grader}{Sept. 2005 - Dec. 2005}
    \begin{itemize}
        \resitem{Graded a first year Astronomy course and provided teaching assistance when required.}
    \end{itemize}

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Memberships}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
    \ressubheading{American Nuclear Society}{{\em 2006 - present}}{Member}{}

\item
    \ressubheading{The Hacker Within}{{\em 2009 - present}}{Member}{}

\item
    \ressubheading{inSCIght: The Scientific Computing Podcast}{{\em 2011 - present}}{Host \& Blogger}{}

\item
    \ressubheading{Software Carpentry}{{\em 2011 - present}}{Member}{}

\item
    \ressubheading{NumFOCUS}{{\em 2011 - present}}{Treasurer}{}

\item
    \ressubheading{American Physical Society}{{\em 2012 - present}}{Member}{}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
    Programming Languages
    \begin{itemize}
        \resitem{{\bf Expert:} Python, Cython, C/C++, BASH}
        \resitem{{\bf Intermediate:} Fortran 77/90/95, Java, JavaScript, Lua, Powersim}
    \end{itemize}

\item
    Markup Languages
    \begin{itemize}
        \resitem{{\bf Expert:} rST, \LaTeX, HTML, CSS}
        \resitem{{\bf Intermediate:} markdown, PHP}
    \end{itemize}

\item
    Specialized Software
    \begin{itemize}
        \resitem{{\bf Expert:} Linux, Unix, OS/2, SSH, HDF5, Boost::Python, NumPy, SciPy, MatPlotLib, ORIGEN v2.2, MCNP5/X, Mathematica, Serpent, Traits, Chaco}
        \resitem{{\bf Intermediate:} MATLAB, Maple, NJOY, Django, web2py, SQLite, MySQL}
    \end{itemize}
\end{itemize}

\end{document}
